Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-02-09 paper-ieee-trans.tex
minor typos in DataGrid

The {\sl DataGrid} \cite{cordis:datagrid} project (Jan 2001 -- Dec 2003) 
had as the main goal to provide scientific communities, including physics, biology and 
earth sciences, with intensive computing and large-scale dataset analysis capabilites.
The project brought together 21 academic and industry partners, from 15 different countries \cite{gagliardi}. 
Grid technology was the emerging technology to be used in order to address these requirements,
thus the project delivered its own software distribution, named EDG (EU {\sl DataGrid}), strongly 
based on Globus middleware services \cite{globus}. The project was organized in 12 workpages, from 
which 5 were devoted to software development coordinated by an 
Architecture Task Force, supervising the overall design and technical consistency 
of the developments.

@@

The authors would like to thanks European Commission with the various funded
projects.

>>>>

The {\sl DataGrid} \cite{cordis:datagrid} project (Jan 2001 -- Dec 2003) 
had as the main goal to provide scientific communities, including physics, biology and 
earth sciences, with intensive computing and large-scale dataset analysis capabilites.
The project brought together 21 academic and industry partners, from 15 different countries \cite{gagliardi}. 
Grid was the emerging technology to be used in order to address these requirements,
thus the project delivered its own software distribution, named EDG (EU {\sl DataGrid}), strongly 
based on Globus middleware services \cite{globus}. The project was organized in 12 work packages, from 
which 5 were devoted to software development coordinated by an 
Architecture Task Force, supervising the overall design and technical consistency 
of the developments.

@@

{\sl INDIGO--DataCloud} project has received funding from the European Research 
Council (ERC) under the European Union's Horizon 2020 research and innovation 
programme (grant agreement n° 777536).
